Wikipedia ngrams Entropy Analysis

### 2019-04-18 ngrams/ngrams.Rmd
making graphs for Psycholing working group talk

```{r setup, include=FALSE}
library(tidyverse)
library(tidytext)
library(tidyboot)
library(entropy)
library(magrittr)
library(feather)
library(here)

library(childesr)

@@

@@

```{r childes}
utterances <- get_utterances(corpus = "Plunkett") %>% 
  filter(speaker_role != "Target_Child") %>%
  rename(words = gloss)

# unigrams to check against previous results
unigrams <- map(2:10, ~ngram_entropy(utterances, .x, 1)) %>% 
  bind_rows()

# bigrams
bigrams <- map(3:10, ~ngram_entropy(utterances, .x, 2)) %>% 
  bind_rows()

# trigrams
trigrams <- map(4:10, ~ngram_entropy(utterances, .x, 3)) %>% 
  bind_rows()

# quadgrams
quadgrams <- map(5:10, ~ngram_entropy(utterances, .x, 4)) %>%
  bind_rows()

unigrams %>%
  bind_rows(bigrams, trigrams, quadgrams) %>%
  mutate(Language = "Danish") %>%
  write_feather("CHILDES/danish_adult.feather")
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(tidytext)
library(tidyboot)
library(entropy)
library(magrittr)
library(feather)
library(here)
library(ggthemes)
library(childesr)

@@

```{r plotting for Monday}
df <- read_feather(here("Data/childes.feather"))

label_data <- data_frame(length = 8, language = "Spanish", gram_order = 6,
                         speaker_role = c("Adult", "Child"), empirical_entropy = c(9,10.25))

df %>% 
  filter(language %in% c("English", "Mandarin", "Spanish"), gram == "bigram", length %in% c(4, 6, 8)) %>%
  ggplot(aes(x = gram_order, y = empirical_entropy, color = speaker_role, label = speaker_role)) + 
  facet_grid(language ~ length, scales = "free") + 
  xlab("Gram position") + 
  ylab("Positional entropy") + 
  geom_pointrange(size = .25, aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_line(size = .25) + 
  theme_classic(base_size = 10) + 
  scale_color_ptol() + 
  theme(legend.position = "nones") + 
  geom_text(data = label_data)

@@

### 2019-04-18 ngrams/wiki_ngrams.Rmd
making graphs for Psycholing working group talk

```{r set up data}
w1 %>% 
  left_join(w2) %>%
  left_join(w3) %>%
  left_join(w4) %>%
  remove_missing() %>%
  slice(1:5) %>%
  melt(id.vars = "Language") %>%
  ggplot(aes(variable, value, color=Language)) + 
  geom_point() +
  geom_line()
```

@@

# let's just try log(sum(abs(s_i))) = language + gram since type/source are all the same atm
## why would there be an interaction between language and gram?
wn <- read_feather(here("Data/wiki_ngrams.feather"))

simple_glm <- glm(data = wn, formula = s_i ~ gram + Language)

@@

wn %>% write_feather(here("Data/wiki_ngrams.feather"))
```

>>>>

@@

# let's just try log(sum(abs(s_i))) = language + gram since type/source are all the same atm
## why would there be an interaction between language and gram?
## shouldn't the final model be more like
# log(sum(abs(s_i))) = language * type + gram * type + (source | type)

wn <- read_feather(here("Data/wiki_ngrams.feather"))

simple_glm <- glm(data = wn, formula = log(s_i) ~ gram + Language)
summary(simple_glm)
```

@@

w1 %>% 
  left_join(w2) %>%
  left_join(w3) %>%
  left_join(w4) %>%
  remove_missing() %>%
  slice(1:5) %>%
  melt(id.vars = "Language") %>%
  ggplot(aes(variable, value, color=Language)) + 
  geom_point() +
  geom_line()
